---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-")
```

# esaj

[![Made In Brazil](https://img.shields.io/badge/made%20in-brazil-green.svg)](http://www.abj.org.br) [![Travis-CI Build Status](https://travis-ci.org/courtsbr/esaj.svg?branch=master)](https://travis-ci.org/courtsbr/esaj) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/courtsbr/esaj?branch=master&svg=true)](https://ci.appveyor.com/project/courtsbr/esaj)

## Overview

The `esaj` R package is a simple interface that allows you to download multiple
kinds of files from Brazil's e-SAJ (Electronic Justice Automation System)
portals. With this package you can save and parse lawsuits, queries, and
decisions with very simple, tidyverse compliant functions.

## Installation

To install `esaj`, run the code below:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("courtsbr/esaj")
```

## Usage

### Lawsuits

Before `esaj` if you wanted to gather information about lawsuits being
processed by Brazil's state-level Judiciary, you would have to go to each
state's e-SAJ portal, manually input each lawsuit's ID, break a capthca, and
only then download an HTML with the information you wanted; now you can simply
run `download_cpopg()` or `download_cposg()`, and spend your valuable time
analysing the data.

```{r, message = FALSE}
# Download first degree lawsuits from multiple states
ids <- c(
  "0123479-07.2012.8.26.0100",
  "0552486-62.2015.8.05.0001",
  "0303349-44.2014.8.24.0020")
esaj::download_cpopg(ids, "~/Desktop/")

# Download second degree lawsuits from São Paulo
ids <- c(
  "1001869-51.2017.8.26.0562",
  "1001214-07.2016.8.26.0565")
esaj::download_cposg(ids, "~/Desktop/")
```

For more information on how to use these functions and which TJs are
implemented, please see [Downloading Lawsuits](http://courtsbr.github.io/esaj/articles/download_lawsuit.html).

### Queries

Besides downloading lawsuits (see the **Downloading Lawsuits** article), `esaj`
also allows the user to download the results of a query on lawsuits. This kind
of query is very useful for finding out what lawsuits contain certain words,
were filed in a given period, were filed in a given court, etc.


```{r}
# Download results of a simple first degree query
esaj::download_cjpg("recurso", "~/Desktop/")

# Download results of a slightly more complex second degree query
esaj::download_cjsg("recurso", "~/Desktop/", classes = c("1231", "1232"))
```

For more information on how to use these functions and all their auxiliary
methods (like `peek_cj*g()` and `cj*g_table()`), please see
[Downloading Queries](http://courtsbr.github.io/esaj/articles/download_query.html).

### Decisions

Of all functions in the `esaj` package, `download_decision()` is probably the
simplest: it downloads the PDF belonging to a decision and that's it.


```{r}
# Download one decision
esaj::download_decision("10000034", "~/Desktop/")

# Download more than one decision
esaj::download_decision(c("10800758", "10000034"), "~/Desktop/")
```

For more information on how to use this function, please see
[Downloading Decisions](http://courtsbr.github.io/esaj/articles/download_decision.html).
