---
title: "Downloading Queries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(esaj)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

Besides downloading lawsuits (see the **Downloading Lawsuits** article), `esaj`
also allows the user to download the results of a query on lawsuits. This kind
of query is very useful for finding out what lawsuits contain certain words,
were filed in a given period, were filed in a given court, etc.

To accomplish this task two functions were made available: `download_cjpg()`
(for queries on first degree lawsuits) and `download_cjsg()` (for queries
on second degree lawsuits). There are also two auxiliary functions that can
help the user to evaluate how long this kind of download might take:
`peek_cjpg()` and `peek_cjsg()`. Finally, there are 3 functions to explore
which arguments to use when calling the functions above: `cjpg_table()`,
`cjsg_table()`, and `browse_table()`.

As of the day of this writing, all aforementioned functions only work with São
Paulo's Justice Court (TJSP).

## Basic usage

To run a query on first degree lawsuits and download the results, simply write
the query as a string and supply the path to the directory where to download all
resulting files. The example below finds all lawsuits containing the word
"recurso".

```{r}
download_cjpg("recurso", "~/Desktop/")
```

As you can see, `download_cj*g()` return the paths to the downloaded files.
The first file always refers to the search page, containing the filled fields
and the first results of the query; the subsequent files contain pages of
results (as many pages as requested by the user).

By default `download_cj*g()` download only one page of results, but we can
also specify page indexes to start and stop downloading.

```{r}
download_cjpg("recurso", "~/Desktop/", min_page = 3, max_page = 6)
```

To help you filter the results even more, many other arguments are also made
available. `download_cjpg()` and `download_cjsg()` have slightly different
ones, so make sure to run `?download_cjpg` or `?download_cjsg` to learn more
about them.

```{r, results = FALSE}
# Repeted arguments
query <- "recurso"
path <- "~/Desktop/"

# First degree query
download_cjpg(query, path, classes = c("8727", "8742"))
download_cjpg(query, path, subjects = "3372")
download_cjpg(query, path, courts = "2-1")
download_cjpg(query, path, date_start = "2016-01-01", date_end = "2016-12-31")

# Second degree query
download_cjsg(query, path, classes = c("1231", "1232"))
download_cjsg(query, path, subjects = "0")
download_cjsg(query, path, courts = "0-56")
download_cjsg(query, path, trial_start = "2009-01-01", trial_end = "2009-12-31")
download_cjsg(query, path, registration_start = "1998-01-01",
              registration_end = "1998-12-31")
```

The output of the calls above are omitted because they are exactly the same.
Despite only `classes` appearing as a character vector, `subjects` and `courts`
also support this kind of input.

An argument not mentioned above is `cores`. This is a very useful tool for
parallelizing the execution of `download_cj*g()` and the value passed on to
it corresponds to the number of processing cores used when downloading the files.

```{r, eval = FALSE}
download_cjpg("recurso", "~/Desktop/", max_page = 10, cores = 4)
```

## Peeking

As you might have guessed, the functions above can take a non-trivial amount of
time to finish executing (specially when there are many pages to download). To
help the user estimate how much time calls to `download_cj*g()` would take,
`peek_cj*g()` were made available.

These functions take the same arguments as `download_cj*g()` (ignoring `path`
and `cores`) and calculate approximatelly how much time it would take to
download all pages of results.

```{r}
peek_cjsg(query, path, classes = c("1231", "1232"))
```

`path` is ignored because the files won't actually be downloaded. `cores` is
ignored because it's very hard to guess how much time is saved by parallelizing
the process, so the estimate only takes one thread into account.

## Tables

Since `download_cj*g()` have very complex arguments, there are 3 other functions
that help the user know which values should be passed on to `classes`,
`subjects`, and `courts`.

`cj*g_table()` take only one argument, `type`, which should be one of
`"classes"`, `"subjects"`, and `"courts"`. They will return tibbles with
all possible values for the corresponding arguments in `download_cj*g()`.

```{r}
dplyr::glimpse(cjpg_table("classes"))
```

Note how the table above has multiple levels, marked 0 through 5. This is
because the class structure is a tree, so higher levels represent classes
closer to the leaves. In the example above, the valid values for the `classes`
argument in `download_cjpg()` are every single number in the `id*` columns.

`cj*g_table("subjects")` have very similar structures to
`cj*g_table("classes")`. `cj*g_table("courts")` have only one level.

To browse `classes` and `subjects` tables, one can also use the `browse_table()`
function. This method uses a list of regex to filter the tibbles returned by
`cj*g_table("classes")` and `cj*g_table("subjects")` more easily than
`dplyr::select()`.

```{r}
table <- cjpg_table("classes")
browse_table(table, list(c("ADM", "CRIMINAL"), "", "", "", "", "Recurso"))
```

For the matching to work properly, `patterns` should be a list of at most 6
character vectors, each one containing either one or a vector of regular
expressions to be applied from left to right on columns `name0` to `name5`.

Note that vectors are ORed and different elements are ANDed. In the example
above, we got back the rows where `name0` contains "ADM" **or** "CRIMINAL"
**and** where `name5` contains "Recurso".
