---
title: "Downloading Lawsuits"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(esaj)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

The `esaj` package has two very useful functions for downloading lawsuits
filed in Brazilian Justice Courts (*Tribunais de Justiça*). The only
arguments you have to provide to them are the lawsuit's unique number
and the directory where to save the downloaded file.

These two functions are called `download_cpopg()` and `download_cposg()`.
The first one works for first degree lawsuits, while the second one works
for second degree lawsuits; despite this superficial difference, both
download lawsuits as HTMLs and return the paths to the downloaded files
in the exact same way.

It's important to note that you shouldn't provide a filename to the `path`
argument. You can pass more than one lawsuit ID to these functions, meaning
that `path` has to contain the directory where all the files should be
downloaded to.

## Basic usage

To download a first degree lawsuits, simply provide the lawsuit's unique number
(ID) and the path to the directory where the file should be saved. The ID doesn't
necessarily have to have all divisor marks, but I'll leave them here for clarity
purposes anyway.

```{r, cache = TRUE}
download_cpopg("0123479-07.2012.8.26.0100", "~/Desktop/")
```

If you want to download more than one lawsuit, provide all IDs in a character
vector and the function will take care of the rest. All lawsuits will be
independently downloaded to the provided directory as if the fuction had been
called once for each ID.

```{r, message = FALSE, cache = TRUE}
ids <- c(
  "0123479-07.2012.8.26.0100",
  "0552486-62.2015.8.05.0001",
  "0303349-44.2014.8.24.0020")
download_cpopg(ids, "~/Desktop/")
```

Note that these lawsuits all belong to different TJs. `download_cpopg()` is
able to identify the Justice Court where the lawsuit was filed and
automatically look for it in the correct website (for a list of all valid TJs
see the  **Implemented TJs** section below).

`esaj` is able to download lawsuits from many TJs because it is capable of
breaking multiple types of captchas (courtesey of the `decryptr` package).
The functions used for this task are not exported, but you can check them
out with `esaj:::download_noc_lawsuit()`, `esaj:::download_bw_lawsuit()`,
and `esaj:::download_rgb_lawsuit()`.

`download_cposg()` works in the exact same way as `download_cpopg()`, but,
as of the day of this writing, it is only able to download lawsuits filed in
São Paulo (TJSP).

```{r, cache = TRUE}
ids <- c(
  "1001869-51.2017.8.26.0562",
  "1001214-07.2016.8.26.0565")
download_cposg(ids, "~/Desktop/")
```

The only case where `download_cposg()` differs in behaviour from
`download_cpopg()` is when the lawsuit turns out to be a list of "closed"
lawsuits. If this ever happens, `download_cposg()` adds some information
to the filenames.

```{r, cache = TRUE}
download_cposg("00000144420138260352", "~/Desktop/")
```

## Implemented TJs

Unfortunately we haven't yet implemented downloaders for all Justice Courts.
These are the ones implemented at the moment:

```{r, echo = FALSE, cache = TRUE}
tjs <- dplyr::tibble(
  Court = c(
    "Acre (AC)", "Alagoas (AL)", "Amapá (AP)", "Amazonas (AM)", "Bahia (BA)",
    "Ceará (CE)", "Distrito Federal (DF)", "Espírito Santo (ES)", "Goiás (GO)",
    "Maranhão (MA)", "Mato Grosso (MT)", "Mato Grosso do Sul (MS)",
    "Minas Gerais (MG)", "Pará (PA) ", "Paraíba (PB)", "Paraná (PR)",
    "Pernambuco (PE)", "Piauí (PI)", "Rio de Janeiro (RJ)",
    "Rio Grande do Norte (RN)", "Rio Grande do Sul (RS)", "Rondônia (RO)",
    "Roraima (RR)", "Santa Catarina (SC)", "São Paulo (SP)", "Sergipe (SE)",
    "Tocantins (TO)"),
  `download_cpopg()` = c(
    rep(FALSE, 3), rep(TRUE, 2), rep(FALSE, 18), rep(TRUE, 2), rep(FALSE, 2)),
  `download_cposg()` = c(rep(FALSE, 24), TRUE, rep(FALSE, 2)))
knitr::kable(tjs)
```
