---
title: "Downloading Decisions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(esaj)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
```

Of all functions in the `esaj` package, `download_decision()` is probably the
simplest. Unlike lawsuit and query functions, there is only one decision
function and absolutelly no helper functions are necessary.

It takes two arguments: a decision unique number (ID) and the path to a
directory. It's important to note that the second argument isn't the path
to a file like `readr::write_*()` functions expect, it's the path to a
folder (which can, but not necessarily has to, exist).

As of this writing, `download_decision()` only works for São Paulo's Justice
Court (TJSP).

## Basic usage

To download a decision, simply call `download_decision()` with a decision ID
and a path. The function will return the path to the downloaded PDF.

```{r}
download_decision("10000034", "~/Desktop/")
```

This function is vectorized, meaning that we can pass it a character vector of
IDs to download more than one decision.

```{r}
download_decision(c("10800758", "10000034"), "~/Desktop/")
```

As expected, it returns the paths to both downloaded PDFs.

It's important to remember that `download_decision()` is breaking captchas in
order to do its job (courtesey of the `decryptr` package). The function tries
at most 10 times to break each captcha, so it's possible that it fails every
time and isn't able to download the decision.

If you find it super necessary to download every single decision, we recommend
using `esaj:::download_decision_()`. With this non-exported function one can
force a larger number of attempts or even get a more verbose output from the
execution.
